\documentclass[]{book} %it is set as default that a chapter starts on right page . to change this pass openany to the additional argument of \documentclass[here]{}
%book offers headings styte by default. i.e, it offers page numbering and chapter\section name in the header of every page excecpt the beginnig of a chapter\section page which has only the page number in the footer

%choosing the style comes first . otherwise it won't work
\pagestyle{myheadings} 
%define myheadings style
%a user defined style which is the same as headings syle
\renewcommand{\chaptermark}[1]{\markboth{\chaptername~\thechapter.#1}{ }}
\renewcommand{\sectionmark}[1]{\markright{\thesection.#1}}
%another style
\renewcommand{\chaptermark}[1]{\markboth{\textbf{(Emon) \thechapter. #1}}{ }}
\renewcommand{\sectionmark}[1]{\markright{\it\large (Chowdhury) \thesection.#1}{ }}



\begin{document}
\chapter*{Preface}
{\Huge books class document comes with twoside printing option as default. \bf while others don't}

\chapter{First Chapter}
%\thispagestyle{empty} %to locally appy empty style in a particular page
{\huge\bf myheadings style is user defined. It works by redefining /chaptermark, /sectionmark, and /subsectionmark with the help of /renewcommand{ }[ ]{ } command.}
	The beginnig of first chapter.
		\section{First Section}
		The start of section one.
			\subsection{First subsection}
			The start of sub-section one.
				\subsubsection{First sub-sub-section}
					The start of sub-sub-section one. Sub-sub-sections are {\bf\Huge not} numbered in case of {\bf\huge article} class.
					\newpage
					....
                    \newpage
                    =====
\chapter{Running Header and Footer}
\bfseries\large
By default, /thispagestyle{plain} is issued by the document-classes of article, book, and report to the 
/maketitle command and the first page of major sectioning commands,like /part{ } or /chapter{ }. 
To suppress the effect of /thispagestyle{plain} on these pages, /thispagestyle{ } with an appropriate
 page style may be used just after the /maketitle, /part{ } or /chapter{ } command, 
 e.g., /thispagestyle{empty} may be used to suppress the default page numbering on these pages.
    \section{1st Section}
    .....
    \newpage
    .....
    \newpage
    \section{2nd Section}
    .........
    \newpage
    ....
    \chapter{3rd Chapter}
    ....
    \newpage
    -----
\end{document}